Positive Results in Registered Reports

### 2020-01-15 appendix/positive_results_SRs_RRs_appendix.Rmd
minor fix to TOST reporting, changed file name

```{r include=FALSE}
source(here("analysis", "02_quantitative_analyses.R"))
```
Of the `r n.SR.round1` standard reports sampled in Round 1,  `r n.support.SR.round1` had positive results, a positive result rate of $`r printnum(prop.support.SR.round1*100)` \%$ ($95 \%$ CI [`r printnum(min(SR.binom.round1$conf.int)*100)`, `r printnum(max(SR.binom.round1$conf.int)*100)`]). 
The difference between this group of standard reports and all Registered Reports ($`r printnum((prop.support.SR.round1-prop.support.RR)*100)` \%$) is thus nearly identical to the one found in the main analysis ($`r printnum((prop.support.SR-prop.support.RR)*100)` \%$). 
Recalculating the one-sided proportions test and the equivalence test (both with an alpha level of $5\%$) shows that this difference is still statistically significant, $\chi^2 = `r printnum(proptestresult.robcheck$statistic)`$, $p `r printp(proptestresult.robcheck$p.value)`$, and still not statistically equivalent to a range between $`r -SESOI*100` \%$ and $`r SESOI*100` \%$, $z = `r printnum(min(tostresult.robcheck$TOST_z1, tostresult.robcheck$TOST_z2))`$, $p `r printp(max(tostresult.robcheck$TOST_p1, tostresult.robcheck$TOST_p2))`$, meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$.
We thus conclude that the decision to replace excluded standard reports by resampling does not affect our results or conclusions in a meaningful way.

>>>>

```{r include=FALSE}
source(here("analysis", "02_quantitative_analyses.R"))
```
Of the `r n.SR.round1` standard reports sampled in Round 1,  `r n.support.SR.round1` had positive results, a positive result rate of $`r printnum(prop.support.SR.round1*100)` \%$ ($95 \%$ CI [`r printnum(min(SR.binom.round1$conf.int)*100)`, `r printnum(max(SR.binom.round1$conf.int)*100)`]). 
The difference between this group of standard reports and all Registered Reports ($`r printnum((prop.support.SR.round1-prop.support.RR)*100)` \%$) is thus nearly identical to the one found in the main analysis ($`r printnum((prop.support.SR-prop.support.RR)*100)` \%$). 
Recalculating the one-sided proportions test and the equivalence test (both with an alpha level of $5\%$) shows that this difference is still statistically significant, $\chi^2 = `r printnum(proptestresult.robcheck$statistic)`$, $p `r printp(proptestresult.robcheck$p.value)`$, and still not statistically equivalent to a range between $`r -SESOI*100` \%$ and $`r SESOI*100` \%$, $z = `r printnum(min(abs(tostresult.robcheck$TOST_z1), abs(tostresult.robcheck$TOST_z2)))`$, $p `r printp(max(tostresult.robcheck$TOST_p1, tostresult.robcheck$TOST_p2))`$, meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$.
We thus conclude that the decision to replace excluded standard reports by resampling does not affect our results or conclusions in a meaningful way.
